Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
fixed references and removed a todo

The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator when investigating contribution quality~\cite{tsay14icse, tasy14fse}.
Thus, both technical factors, which describe the complexity of the commit, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

@@

\vspace{1ex}
\noindent\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:folowerSuccess}, we compare the relationship
between a developer's followers and the build integration success.

>>>>

The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator when investigating contribution quality~\cite{tsay14icse, tsay14fse}.
Thus, both technical factors, which describe the complexity of the commit, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

@@

\vspace{1ex}
\noindent\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
between a developer's followers and the build integration success.
